---
title: "Notes from: Modeling Evolution - an introduction to numerical methods"
author: "Karly J. Ross"
date: "16/07/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About this document

This document is a compilation of my notes and review and self study from the text "Modeling Evolution" by Derek A. Roff.  The purpouse of the project is to revise what I have learned about mathimatical modles of evolution and enhance and imporve my skills in using R. As I work through the chapters I will include the code from the text book in the notes, as well as the code I create independatly.   By the end of this exercise I will also be comfortable using R markdown. 

##Chapter 1\

*Notes from the First Chapter*

*Code from the first chapter*

```{r cars}
summary(cars)
```
*Code produced independatly*

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
